Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-09 ms.qmd
Minor change
Updates to lnRR on new files from Alex

To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiogical traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude. We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat). We used non-linear tensors for latitude and longitude as any response could be complicated by local factors. Our model included random effects of species, trait, phylogeny and study. We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude. To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1$^{\circ}$C change as opoosed to 10$^{\circ}$C as follows:

@@

# Create a match column.
climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))

>>>>

To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiogical traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude. We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat). We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude). Our model included random effects of species, trait, phylogeny and study. We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude. To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1$^{\circ}$C change as opoosed to 10$^{\circ}$C as follows:

@@

# Bring in Climate data
climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")

# Create a match column.
climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
